---
title: "02 R and Transform Data Starter Code"
format: docx
editor: visual
---

## Lecture 02 Notes

### R/R Studio Orientation

```{r}

# Try copying and running this code in the Console.

5+5
```

```{r}

# This Quarto document is in your Source window. Try running this code chunk by pressing the green arrow.

print(2 * (18 - 7))
```

```{r}

# Try adding your own comment here and see if it changes the output at all.

# 

print(2 * (18 - 7))
```

```{r}

# Try saving this variable to your Environment.

variable <- 100
```

```{r}

# Seek Help with the 'mean' function.

help(mean)
```

### The Tidyverse

```{r}

# Before runnning this code, you need to install the tidyverse package. Click Tools at the top of the screen, then Install Packages, and enter tidyverse. Then load the package here.

library(tidyverse)
```

### Import CSV Files

```{r}

# Ensure that you're in the right working directory (folder). You should see customer_data.csv in your Files tab on the right.

customer_data <- read_csv("customer_data.csv", show_col_types = FALSE)
```

### Data Frames

```{r}

# This code displays the data frame.

customer_data
```

```{r}

# This code gives us an overview of what our data looks like.

glimpse(customer_data)
```

### Filter Observations

```{r}

# This code displays only customers with a college degree.

filter(customer_data, college_degree == "Yes")
```

```{r}

# This code displays only customers outside of the West region.

filter(customer_data, region != "West")
```

```{r}

# This code displays only female customers with an annual income of over $70,000.


filter(customer_data, gender == "Female", income > 70000)
```

### Your Turn!

```{r}

# Write code that filters to only display married customers born before 1995.

```

### Slice Observations

```{r}

# This code displays only the first 5 customers in the data frame.


slice(customer_data, 1:5)
```

### Arrange Observations

```{r}

# This code displays the customers in order of birth year.

arrange(customer_data, birth_year)
```

```{r}

# This code arranges them from youngest to oldest.

arrange(customer_data, desc(birth_year))
```

### Select Variables

```{r}

# This code selects all the columns from region to review_text.

select(customer_data, region:review_text)
```

### Mutate Variables

```{r}

# This code changes the income column to be in terms of 1000s of dollars.

mutate(customer_data, income = income / 1000)
```

### Join Data Frames

```{r}

# This will read in the transaction data (again, ensure that you're in the right working directory)

store_transactions <- read_csv("store_transactions.csv")
```

```{r}

glimpse(store_transactions)
```

```{r}

left_join(customer_data, store_transactions, join_by(customer_id))
```

```{r}

inner_join(customer_data, store_transactions, join_by(customer_id))
```

### Consecutive Lines of Code

```{r}

# Try out the pipe operator!

customer_data |> 
  filter(credit == 850, state == "WY")
```

### Your Turn!

```{r}

# Add comments between each line to explain what this code is doing!

customer_data |> 
  left_join(store_transactions, join_by(customer_id)) |> 
  filter(region == "West", feb_2005 == max(feb_2005)) |> 
  mutate(age = 2026 - birth_year) |> 
  select(age, feb_2005) |> 
  arrange(desc(age)) |> 
  slice(1)
```

### Live Coding Exercise

Now that we've built up a lot of skills, let's try applying them together. Recall that you are an analyst for Patagonia. Imagine your manager wants a list of the 15 most valuable customers in the Midwest region. How should we define "valuable," and how would we come up with that list?

```{r}

# take notes and code along here
```
