---
title: "Exercise 02 Solution"
format: docx
editor: visual
---

## Exercise 2

In RStudio, create a new Quarto document, load the tidyverse, and import the data. Don't forget to ensure that a copy of your data files is in your working directory! Then, using the `|>` in consecutive lines of code, find the customers who have spent the most recently by doing the following.

1.  Join the `customer_data` and `store_transactions` data.

2.  Only keep customers in the `South`.

3.  Create a new variable `age` using `2026 - birth_year`.

4.  Only keep the variables `age`, `gender`, `income`, `credit`, `married`, `college_degree`, `region`, and `dec_2018`.

5.  Arrange the data in descending order based on `dec_2018` transactions.

6.  Keep the top 3 rows of data.

7.  Who appears to be purchasing the most items for that month in the South?

8.  Render the Quarto document as a Word Doc and upload to Canvas.

Five points total, one point each for:

\- Loading the tidyverse.

\- Importing customer_data and store_transactions.

\- Following the instructions using consecutive lines of code.

\- Making a reasonable attempt to follow all of the steps and answer the question.

\- Submitting a rendered Word doc.

```{r}

# Load packages.

library(tidyverse)
```

```{r}

# Import data.

customer_data <- read_csv("customer_data.csv", show_col_types = FALSE) 
store_transactions <- read_csv("store_transactions.csv", show_col_types = FALSE)
```

```{r}

# Find the customers who have spent the most recently.

customer_data |> left_join(store_transactions, join_by(customer_id)) |> filter(region == "South") |> mutate(age = 2024 - birth_year) |> select(age, gender:region, dec_2018) |> arrange(desc(dec_2018)) |> slice(1:3)
```

Customers in the South who purchased the most in December 2018 appear to be mostly married with college degrees.
